Figure 1 - overview

### 2024-07-09 ms_figure_1_overview.Rmd
Indicate meiosis-specific TFs in Fig 1

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color),
                       name = "") + 
    scale_x_discrete(breaks = c("mei4", "atf31", "atf21", "cuf2", "rsv1")) + 
    guides(color = guide_legend(nrow = 2, byrow = TRUE)) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + theme(axis.text.x = element_blank(),
                axis.ticks.length.x = unit(2, "mm"),
                axis.ticks.x = element_line(color = main_colors[1],
                                            linewidth = 1.25)))
```

>>>>

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)", 
                   "Meiosis-specific transcription factors")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled, shape = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1, show.legend = TRUE) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color,
                                  "Meiosis-specific transcription factors" = main_colors[1]),
                       drop = FALSE, name = "") + 
    scale_shape_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = 16,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = 16,
                                  "Meiosis-specific transcription factors" = 15),
                       drop = FALSE, name = "") + 
    scale_x_discrete(breaks = c("mei4", "atf31", "atf21", "cuf2", "rsv1")) + 
    guides(color = guide_legend(nrow = 3, byrow = TRUE,
                                override.aes = list(size = 3))) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + theme(axis.text.x = element_blank(),
                axis.ticks.length.x = unit(2, "mm"),
                axis.ticks.x = element_line(color = main_colors[1],
                                            linewidth = 1.25)))
```
